---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# regional

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/regional)](https://CRAN.R-project.org/package=regional)
[![R-CMD-check](https://github.com/Nowosad/regional/workflows/R-CMD-check/badge.svg)](https://github.com/Nowosad/regional/actions)
[![Codecov test coverage](https://codecov.io/gh/Nowosad/regional/branch/master/graph/badge.svg)](https://codecov.io/gh/Nowosad/regional?branch=master)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/regional)](https://cran.r-project.org/package=regional)
<!-- badges: end -->

The **regional** package calculates intra-regional and inter-regional similarities based on user-provided spatial vector objects (regions) and spatial raster objects (cells with values).
Implemented metrics include inhomogeneity, isolation (Haralick and Shapiro (1985), https://doi.org/10.1016/S0734-189X(85)90153-7>, Jasiewicz et al. (2018), https://doi.org/10.1016/j.cageo.2018.06.003), and distinction (Nowosad (2021), https://doi.org/10.1080/13658816.2021.1893324).

## Installation

You can install the released version of regional from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("regional")
```

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("Nowosad/regional")
```

## Example

```{r, message=FALSE}
library(regional)
library(terra)
library(sf)
volcano = rast(system.file("raster/volcano.tif", package = "regional"))
vr = read_sf(system.file("regions/volcano_regions.gpkg", package = "regional"))
plot(volcano)
plot(vect(vr), add = TRUE)
```

### Inhomogeneity

How much internally inconsistent each region is?

```{r}
vr$inh = reg_inhomogeneity(vr, volcano, sample_size = 0.5)
plot(volcano)
plot(vr["inh"], add = TRUE)
mean(vr$inh)
```

### Isolation

How much the focus region differs from its neighbors?

```{r}
vr$iso = reg_isolation(vr, volcano, sample_size = 1)
plot(volcano)
plot(vr["iso"], add = TRUE)
mean(vr$iso)
```

## Contribution

Contributions to this package are welcome - let me know if you need other distance measures or transformations, have any suggestions, or spotted a bug. 
The preferred method of contribution is through a GitHub pull request. 
Feel also free to contact us by creating [an issue](https://github.com/nowosad/regional/issues).

